Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
done pages 5 and 8

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

\item[$\bullet$] $J\in\I_\P$ is the set over which holes are indexed.
$I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$
\item[$\bullet$] $S_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
hole $j$.

@@

By lack of space, we have omitted here the formal (structural)
definition of $Sorts$ (the 
set of actions of a hole or a pNet), $Leaves$ and $Holes$ (all pLTSs
(resp holes) in a pNet hierarchical system. These can be found in \cite{henrio:Forte2016}.
%The preceding definition relies on the auxiliary functions below:

@@

\paragraph{Structural Semantic Rules:}
Now we build the semantics of an open pNet as an open automaton where
LTSs are the pLTSs at 
the leaves of the pNet structure, and the states are structured as in
the previous section. 
%given by Definition~\ref{def-states}.
The open transitions first
 project the global state into states of the leaves, then apply
pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
%structure does not appear in the open-automaton, only the
%set of Holes and the set of Leaves.
The semantics   regularly instantiates \emph{fresh} variables, and uses a
\emph{clone} operator that clones a term replacing each variable with a
fresh one.

@@

\paragraph{Fresh variables management.}
The variables in each synchronization vector are considered local:
for a given pNet expression, we must have fresh local variables for
each occurrence of a vector (= each time we instantiate rule
Tr2). Similarly the state variables of each copy of a
given pLTS in the system, must be distinct, and those created for each
application of Tr2 have to be fresh and all distinct. 
% This will be implemented within the open-automaton generation algorithm,
% e.g. using name generation using a global counter as a suffix.

>>>>

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure which leaves are pLTSs and holes:\\
$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

\item[$\bullet$] $J\in\I_\P$ is the set over which holes are indexed.
$I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$

\item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
  denoting the $\Sort$\footnote{The formal definition of $Sorts$ (set of actions of a Hole
  or pNet), $Leaves$ and $Holes$ (all pLTSs (resp holes) in a pNet
  hierarchical system. These can be found in \cite{henrio:Forte2016}.}
  of hole $j$.

@@

%The preceding definition relies on the auxiliary functions below:

@@

\paragraph{Structural Semantic Rules:}
Now we build the semantics of an open pNet as an open automaton where
LTSs are the pLTSs at 
the leaves of the pNet structure, and the states are structured as in
the previous section. 
%given by Definition~\ref{def-states}.
The open transitions first
 project the global state into states of the leaves, then apply
pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
%structure does not appear in the open-automaton, only the
%set of Holes and the set of Leaves.
The semantics   regularly instantiates \emph{fresh} variables, and uses a
\emph{clone} operator that clones a term replacing each variable with a
fresh one.
The variables in each synchronization vector are considered local:
for a given pNet expression, we must have fresh local variables for
each occurrence of a vector (= each time we instantiate rule
Tr2). Similarly the state variables of each copy of a
given pLTS in the system, must be distinct, and those created for each
application of Tr2 have to be fresh and all distinct.

@@

%\paragraph{Fresh variables management.}

% This will be implemented within the open-automaton generation algorithm,
% e.g. using name generation using a global counter as a suffix.
